{\bf {\Large Evaluation and correction of noise related to physical processes in estimates of estuary metabolism}}

### 2014-08-14 swmp_noise.Rnw
finished tables/figs for simulation assessment after detiding worked

% example of creating simulated time series
\centering\vspace*{\fill}
<<do_sim, eval = T, echo = F, cache = T, fig.width = 8, fig.height = 7, eval.after='fig.cap', fig.cap = 'Example of creating a simulated \\ac{DO} time series.  Simulated values were estimated every thirty minutes for 31 days.  Yellow indicates daylight periods.'>>=
# create time vector
vec <- c('2014-05-01 00:00:00', '2014-05-31 00:00:00')
vec <- as.POSIXct(vec, format = '%Y-%m-%d %H:%M:%S')
vec <- seq(vec[1], vec[2], by = 60*30)

@@

# create simulated time series of DO, tide, etc.
DO_sim <- ts_create(
  vec, 
  do.amp = 2, 
  tide_cat = 'Mixed Semidiurnal', 
  tide_assoc = 4,
  err_rng_obs = 2, 
  err_rng_pro = 2, 
  seeded = T
  )  
prd_tmp <- wtreg_fun(DO_sim)
prd_tmp$DO_res <- with(prd_tmp, DO_obs - DO_prd)

levs <- c('DO_obs', 'DO_prd', 'DO_nrm', 'DO_res', 'DO_dtd')
to.plo <- melt(prd_tmp, id.var = c('Day', 'sunrise'),
  measure.var = levs
  )
to.plo$variable <- factor(to.plo$variable, levels = levs)

facet_wrap_labeller(p, labels = c(
  expression(italic(DO [obs])),
  expression(italic(DO [tid])),
  expression(italic(DO [mtd])),
  expression(italic(
    paste(DO [res], '=', DO [obs] - DO [tid]))),
  expression(italic(
    paste(DO [dtd], '=', DO [mtd] + DO [res])))
  ))

@@

% example of error surfaces 
\centering\vspace*{\fill}
<<err_surf, fig.height = 6, fig.width = 6, cache = T, echo = F, eval = T, fig.cap = 'Examples of correlations (left) and errors (right) between detided and biological \\ac{DO} from weighted regression results.  Each tile represents a correlation or error value from results for a given combination of simulation parameters ($DO_{adv}$, $DO_{die}$, $\\epsilon_{pro}$, $\\epsilon_{obs}$) and selected window widths (two and ten days).  Results are for simulations using a diurnal tidal time series.'>>=

sel_vec <- with(comb_grd,
  tide_cat %in% 'Diurnal' &
  dec_win %in% c(1, 5)
  )

comb_tmp <- comb_grd[sel_vec, ]
prd_tmp <- prdnrm[sel_vec]

rm('prdnrm')

# get err comps for pred/obs and norm/bio
errs_all <- NULL

jitt <- rnorm(nrow(prd_tmp[[1]]), 0, 1e-10)
for(i in 1:length(prd_tmp)){

  x <- prd_tmp[[i]]

  dtd_cor <- cor(x$DO_bio + jitt, x$DO_dtd + jitt)

  dtd_err <- rmse(x$DO_bio + jitt, x$DO_dtd + jitt)

  errs_all <- rbind(errs_all, data.frame(dtd_cor, dtd_err))

# reassign factor labels for bio amp and tidal assoc
to_plo <- data.frame(comb_tmp, errs_all)
labs <- paste('Bio Amp',unique(to_plo$bio_rng))
to_plo$bio_rng <- factor(to_plo$bio_rng, labels = labs)
labs <- paste('Assoc',unique(to_plo$tide_assoc))
to_plo$tide_assoc <- factor(to_plo$tide_assoc, labels = labs)
labs <- paste('Window',unique(to_plo$dec_win))
to_plo$dec_win <- factor(to_plo$dec_win, labels = labs)

# setup facet labels
facet1_names <- list(
  'Assoc 0' = expression(paste(italic(DO [adv]), ' 0')), 
  'Assoc 1' = expression(paste(italic(DO [adv]), ' 1')),
  'Assoc 2' = expression(paste(italic(DO [adv]), ' 2'))
  )
facet2_names <- list(
  'Window 1' = 'Window 2', 
  'Window 5' = 'Window 10'
  )
facet3_names <- list(
  'Bio Amp 0' = expression(paste(italic(DO [bio]), ' 0')), 
  'Bio Amp 1' = expression(paste(italic(DO [bio]), ' 1')),
  'Bio Amp 2' = expression(paste(italic(DO [bio]), ' 2'))
  )
plot_labeller <- function(variable,value){
  if (variable=='tide_assoc')
    return(facet1_names[value])
  if (variable=='dec_win')
    return(facet2_names[value])
  if (variable=='bio_rng')
    return(facet3_names[value])
  }

p1 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), 
    z = dtd_cor, fill = dtd_cor)) +
  geom_tile() + 
  facet_grid(dec_win + bio_rng ~ tide_assoc, scales = 'free', 
    labeller = plot_labeller) +
  scale_fill_gradientn(limits = c(0.7, 1), name = 'Correlation', 
    colours = brewer.pal(11, 'Spectral')) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) +
  theme_bw() +
  theme(legend.position = 'top')

p2 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), 
    z = dtd_err, fill = dtd_err)) +
  geom_tile() + 
  facet_grid(dec_win + bio_rng ~ tide_assoc, scales = 'free', 
    labeller = plot_labeller) +
  scale_fill_gradientn(limits = c(0, 1.05), name = 'RMSE', 
    colours = brewer.pal(11, 'Spectral')) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) +
  theme_bw() +
  theme(legend.position = 'top')

grid.arrange(p1, p2, ncol = 2)
@
\vfill
\clearpage

% example of extreme scenario
\centering\vspace*{\fill}
<<extreme, eval = T, echo = F, cache = T, fig.width = 7, fig.height = 6.5, fig.cap = 'An extreme example of results from the weighted regression with decreasing window widths.  Results are for a simulated time series with a diurnal tidal component, no effect of tidal advection ($DO_{adv} = 0$), and an observed \\ac{DO} signal dominated only by a diel component ($DO_{bio} = 2$, $\\epsilon_{obs} = 0$, $\\epsilon_{pro} = 0$).  Window widths varied form 2 to 40 days.  See \\cref{do_tid,do_mtd,do_dtd,do_obs} for notation.'>>=
######
# examples of how detiding works

@@

% summary of simulation performance for detided and biological
<<dtd_perf, cache = F, echo = F, eval = T, results = 'asis'>>=

@@

# calculate mean, se for dtd_cor and dtd_err
dtd_perf <- llply(names(mod_perf)[1:6],
  .fun = function(x) {
    ddply(
      mod_perf,
      .variables = x,
      .fun = function(y) {
        c(
          mean(y$dtd_cor),
          sd(y$dtd_cor)/sqrt(length(y)),
          mean(y$dtd_err),
          sd(y$dtd_err)/sqrt(length(y))
        )
    })}
  )
# multiply windows by two since value is half window width
dtd_perf[[6]]$dec_time <- 2*dtd_perf[[6]]$dec_time
# rename first column for combining, create column for parameter,  then combine
dtd_perf <- lapply(dtd_perf, 
  function(x) { 
    Parameter <- names(x)[1]
    names(x)[1] <- 'Level'
    x[,1] <- factor(x[,1])
    Parameter <- rep(Parameter, nrow(x))
    x <- data.frame(Parameter, x)
    x
    }
  )
dtd_perf <- do.call('rbind', dtd_perf)
names(dtd_perf) <- c('Parameter', 'Level', 'Mean cor', 'Se cor', 'Mean err', 'Se err')

# names for row categories in table
Parms <- c('Tidal category', '$\\boldsymbol{DO_{die}}$', 
  '$\\boldsymbol{DO_{adv}}$',  
  '$\\boldsymbol{\\epsilon_{pro}}$', 
  '$\\boldsymbol{\\epsilon_{obs}}$', 
  'Window')
tab <- form_fun(dtd_perf[, -c(1:2)])
rows <- dtd_perf[, 2]
cap.val<-'Mean correlations and error estimates between detided and biological \\ac{DO} time series for different simulation parameters (tidal category, $DO_{die}$, $DO_{adv}$, $\\epsilon_{pro}$, $\\epsilon_{obs}$) and window widths (days).  Each value represents a combination of results from multiple simulations with the parameter value held constant for each row (e.g., row one is a summary of all simulations for which the tidal category was diurnal).'

@@

latex( 
  tab,
  file = '',
  rowlabel = 'Parameter',
#   insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = Parms,
  n.rgroup = c(rep(3, 5), 5),
  cgroup = c('Correlation', 'RMSE'),
  n.cgroup = c(2, 2),
  rowname = rows,
  colheads=rep(c('Mean','Std. Err.'),2),
  label = 'tab:dtd_perf'
  )

@@

% correlations with tide before/after wtreg
<<cor_res, cache = F, echo = F, eval = T, results = 'asis'>>=
# ######
# # table of DO/metab correlations before after, detiding
# # note that tide in met_ls is daily average of hourly tidal change
# 
# # metab and inst flux data
# load('met_ls.RData')
# load('met_ls_inst.RData')
# load('case_grds.RData')
# 
# # go through each site for DO cors, use metab list for metab cors
# case_regs <- list.files(getwd(), '_wtreg_[0-9]*.RData')
# cor_res <- alply(matrix(case_regs),
#   1, 
#   .fun = function(x){
#   
#     # load wtreg data
#     load(x)
#     nm <- gsub('.RData', '', x)
#     dat_in <- get(nm)
#       
#     # DO obs v tide
#     do_obs <- with(dat_in, 
#       cor.test(DO_obs, Tide)
#       )
#     
#     # DO dtd v tide
#     do_dtd <- with(dat_in, 
#       cor.test(DO_dtd, Tide)
#       )
#     
#     # inst flux data
#     flux_in <- met_ls_inst[[x]]
#     
#     # DOF with dtide
#     flux_obs <- with(flux_in, 
#       cor.test(DOF_obs, dTide)
#       )
#     
#     # DOF_dtd with dtide
#     flux_dtd <- with(flux_in, 
#       cor.test(DOF_dtd, dTide)
#       ) 
#     
#     # get tidal range for metabolic day/night periods from flux_in
#     # for correlation with daily integrated metab
#     tide_rngs <- ddply(flux_in, 
#       .variables = c('met.date'),
#       .fun = function(x){
# #         sunrise <- suppressWarnings(diff(range(x[x$variable %in% 'sunrise', 'Tide'])))
# #         sunset <- suppressWarnings(diff(range(x[x$variable %in% 'sunset', 'Tide'])))
# #         if(sunrise == 'Inf') sunrise <- NA
# #         if(sunset == 'Inf') sunset <- NA
# #         daytot <- diff(range(x$Tide))
#         sunrise <- mean(diff(x[x$variable %in% 'sunrise', 'Tide'], na.rm = T))
#         sunset <- mean(diff(x[x$variable %in% 'sunset', 'Tide'], na.rm = T))
#         if(sunrise == 'Inf') sunrise <- NA
#         if(sunset == 'Inf') sunset <- NA
#         daytot <- mean(diff(x$Tide, na.rm = T))
#         
#         c(daytot, sunrise, sunset)
#         }
#       )
#     names(tide_rngs) <- c('Date','daytot', 'sunrise', 'sunset')
#     
#     # get metab data from list
#     dat_in <- met_ls[[x]]
#     dat_in <- merge(dat_in, tide_rngs, by = 'Date', all.x = T)
#     
#     # as list for all metab correlations
#     # Pg values correlated with tidal range during sunlight hours
#     # Rt values correlated with tidal range during night hours
#     # NEM values correlated with metabolic daily tidal range
#     met_cor <- list(
#       
#       Pg_obs = with(dat_in, 
#         cor.test(Pg, sunrise)
#         ),
#     
#       Rt_obs = with(dat_in, 
#         cor.test(Rt, sunset)
#         ),
#     
#       NEM_obs = with(dat_in, 
#         cor.test(NEM, daytot)
#         ),
#     
#       Pg_dtd = with(dat_in, 
#         cor.test(Pg_dtd, sunrise)
#         ),
#     
#       Rt_dtd = with(dat_in, 
#         cor.test(Rt_dtd, sunset)
#         ),
#     
#       NEM_dtd = with(dat_in, 
#         cor.test(NEM_dtd, daytot)
#         )
#       
#       )
#     
#     # DO and metab corrs combined
#     all_ls <- c(do_obs = list(do_obs), do_dtd = list(do_dtd),
#       flux_obs = list(flux_obs), flux_dtd = list(flux_dtd), met_cor)
#     
#     # convert the stats for each wtreg to data frame
#     res_sum <- ldply(all_ls, 
#       function(x) with(x, c(estimate, p.value))
#       )
#     names(res_sum) <- c('var', 'cor', 'pval')
# 
#     res_sum
#     
#   })
# names(cor_res) <- case_regs
# 
# # melt and make separate columns for site and window comb value
# cor_res <- melt(cor_res, id.var = names(cor_res[[1]]))  
# cor_res$site <- gsub('_wtreg_[0-9]*.RData', '', cor_res$L1)
# cor_res$wins <- as.numeric(gsub('^.*_wtreg_|.RData', '', cor_res$L1))
# 
# # merge with case_grds
# case_grds$wins <- as.numeric(row.names(case_grds))
# cor_res <- merge(cor_res, case_grds, by = 'wins', all.x = T)
# 
# # create columns for variable (DO, flux, etc.) and sub variable (obs, dtd)
# cor_res$sub_var <- gsub('^.*_', '', cor_res$var)
# cor_res$var <- gsub('_.*$', '', cor_res$var)
# 
# save(cor_res, file = 'cor_res.RData')
# 
# to_plo <- cor_res
# to_plo$group_var <- paste(to_plo$Tide, to_plo$sub_var)
# to_plo_obs <- to_plo[to_plo$sub_var %in% 'obs', ]
# p1 <- ggplot(to_plo[to_plo$sub_var %in% 'dtd',], 
#     aes(x = factor(Day), y = cor, colour = Tide, group = group_var)) +
#   geom_line() + 
#   geom_line(data = to_plo_obs, 
#     aes(x = factor(Day), y = cor, group = group_var), 
#     colour = 'black', size = 1) +
#   geom_point(aes(pch = sub_var)) +
#   facet_grid(var ~ site) +
#   ylim(c(-1, 1)) +
#   theme_bw()

@@

# subset cor_res for window of 30 days, tidal prop 1
cor_res <- cor_res[with(cor_res, Tide == 1 & Day == 30), ]

@@

# reorder rows, columns for plot
to_tab$sub_var <- factor(to_tab$sub_var, levels = c('obs', 'dtd'))
to_tab <- to_tab[with(to_tab, order(site, sub_var)), ]
to_tab <- to_tab[, c('site', 'sub_var', 'do', 'flux', 'Pg', 'Rt', 'NEM')]

@@

# reorder rows, columns for plot
pvals$sub_var <- factor(pvals$sub_var, levels = c('obs', 'dtd'))
pvals <- pvals[with(pvals, order(site, sub_var)), ]
pvals <- pvals[, c('site', 'sub_var', 'do', 'flux', 'Pg', 'Rt', 'NEM')]

>>>>

\section{Figures}

# create simulated time series of DO, tide, etc.
DO_sim <- ts_create(
  vec, 
  do.amp = 2, 
  tide_cat = 'Mixed Semidiurnal', 
  tide_assoc = 4,
  err_rng_obs = 2, 
  err_rng_pro = 2, 
  seeded = T
  )  
prd_tmp <- wtreg_fun(DO_sim, wins = list(6, 12, 1))

levs <- c('DO_obs', 'DO_prd', 'DO_nrm')
to.plo <- melt(prd_tmp, id.var = c('Day', 'sunrise'),
  measure.var = levs
  )
to.plo$variable <- factor(to.plo$variable, levels = levs)

facet_wrap_labeller(p, labels = c(
  expression(italic(DO [obs])),
  expression(italic(DO [tid])),
  expression(italic(DO [nrm]))
  ))

% example of creating simulated time series
\centering\vspace*{\fill}
<<do_sim, eval = T, echo = F, cache = T, fig.width = 8, fig.height = 7, eval.after='fig.cap', fig.cap = 'Example of creating a simulated \\ac{DO} time series.  Values were simulated every 30 minutes for 30 days.  Yellow indicates daylight periods.'>>=
# create time vector
vec <- c('2014-05-01 00:00:00', '2014-05-31 00:00:00')
vec <- as.POSIXct(vec, format = '%Y-%m-%d %H:%M:%S')
vec <- seq(vec[1], vec[2], by = 60*30)

@@

@@

% example of error surfaces 
\centering\vspace*{\fill}
<<err_surf1, fig.height = 7, fig.width = 6, cache = T, echo = F, eval = T, fig.cap = "Correlations and errors (\\ac{RMSE}) for detided \\ac{DO} time series, $DO_{dtd}$, from weighted regression with `true' biological \\ac{DO}, $DO_{bio}$, for varying simulation parameters: tidal category (e.g., Mixed), strength of tidal association with \\ac{DO} signal $DO_{adv}$, amount of process uncertainty $\\epsilon_{pro}$, amount of observation observation uncertainty $\\epsilon_{obs}$, and strength of diel \\ac{DO} component $DO_{die}$.  Each tile represents the correlation or error between detided and biological \\ac{DO} time series from results for a given combination of simulation parameters.  Results are averaged for all window widths used to evaluate the regressions.">>=

# load summary of model performance for simulations
load('mod_perf.RData')

to_plo <- mod_perf

# aggregate for simpler plot
to_plo <- ddply(
  to_plo, 
  .variable = c('tide_cat','bio_rng', 'tide_assoc', 'err_rng_pro', 'err_rng_obs'),
  .fun = function(x) data.frame(cor = mean(x$cor), err = mean(x$err))
  )

# reassign factor labels for bio amp and tidal assoc
labs <- c('Diurnal', 'Semid.', 'Mixed')
to_plo$tide_cat <- factor(to_plo$tide_cat, levels = c('Diurnal', 
  'Semidiurnal', 'Mixed Semidiurnal'), labels = labs)
labs <- paste('Bio Amp', unique(to_plo$bio_rng))
to_plo$bio_rng <- factor(to_plo$bio_rng, labels = labs)
labs <- paste('Assoc',unique(to_plo$tide_assoc))
to_plo$tide_assoc <- factor(to_plo$tide_assoc, labels = labs)

# setup facet labels
facet1_names <- list(
  'Diurnal' = 'Diurnal',
  'Semid.' = 'Semid.',
  'Mixed' = 'Mixed'
  )
facet2_names <- list(
  'Bio Amp 0' = expression(paste(italic(DO [die]), ' 0')), 
  'Bio Amp 1' = expression(paste(italic(DO [die]), ' 1')),
  'Bio Amp 2' = expression(paste(italic(DO [die]), ' 2'))
  )
facet3_names <- list(
  'Assoc 0' = expression(paste(italic(DO [adv]), ' 0')), 
  'Assoc 1' = expression(paste(italic(DO [adv]), ' 1')),
  'Assoc 2' = expression(paste(italic(DO [adv]), ' 2'))
  )

plot_labeller <- function(variable,value){
  if (variable=='tide_cat')
    return(facet1_names[value])
  if (variable=='tide_assoc')
    return(facet2_names[value])
  if (variable=='bio_rng')
    return(facet3_names[value])
  }

mat_theme <-   theme(
    panel.margin = unit(0, 'lines'), 
    strip.text = element_text(size = 8),
    legend.text = element_text(size = 8),
    legend.position = 'top',
    axis.text = element_text(size = 8)
    )

p1 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(tide_cat + bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(11, 'Spectral'), limits = c(0, 1)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(tide_cat + bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = brewer.pal(11, 'Spectral'), limits = c(0, 2.5)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

grid.arrange(p1, p2, ncol = 2)

% example of error surfaces 
\centering\vspace*{\fill}
<<err_surf2, fig.height = 2.33, fig.width = 6, cache = T, echo = F, eval = T, fig.cap = "Correlations and errors (\\ac{RMSE}) for detided \\ac{DO} time series, $DO_{dtd}$, from weighted regression with `true' biological \\ac{DO}, $DO_{bio}$, for varying half window widths: days, hour of day, and proportion of tidal range.  Each tile represents the correlation or error between detided and biological \\ac{DO} time series from results for a given combination of window widths.  Results are averaged for all simulation parameters used to evaluate the regressions.">>=

# load summary of model performance for simulations
load('mod_perf.RData')

to_plo <- mod_perf

# aggregate for simpler plot
to_plo <- ddply(
  to_plo, 
  .variable = c('dec_time', 'hour', 'Tide'),
  .fun = function(x) data.frame(cor = mean(x$cor), err = mean(x$err))
  )

# reassign factor labels for windows
labs <- paste('Tide', unique(to_plo$Tide))
to_plo$Tide <- factor(to_plo$Tide, labels = labs)

mat_theme <-   theme(
    panel.margin = unit(0, 'lines'), 
    strip.text = element_text(size = 8),
    legend.text = element_text(size = 8),
    legend.position = 'top',
    axis.text = element_text(size = 8)
    )

p1 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(11, 'Spectral'), limits = c(0.3, 0.7),
    breaks = seq(0.3, 0.7, by = 0.1)
    ) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  xlab('Hours') +
  ylab('Days') + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = brewer.pal(11, 'Spectral'), limits = c(1, 1.5), 
    labels = format(seq(1, 1.5, by = 0.1), nsmall = 1)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab('Hours') +
  ylab('Days') + 
  theme_bw() +
  mat_theme

grid.arrange(p1, p2, ncol = 2)

% example of extreme scenario
\centering\vspace*{\fill}
<<extreme, eval = F, echo = F, cache = T, fig.width = 7, fig.height = 6.5, fig.cap = 'An extreme example of results from the weighted regression with decreasing window widths.  Results are for a simulated time series with a diurnal tidal component, no effect of tidal advection ($DO_{adv} = 0$), and an observed \\ac{DO} signal dominated only by a diel component ($DO_{bio} = 2$, $\\epsilon_{obs} = 0$, $\\epsilon_{pro} = 0$).  Window widths varied form 2 to 40 days.  See \\cref{do_tid,do_mtd,do_dtd,do_obs} for notation.'>>=
######
# examples of how detiding works

@@

\section{Tables}

% summary of simulation performance for detided and biological, sim parameters
<<dtd_perf1, cache = F, echo = F, eval = T, results = 'asis'>>=

@@

# calculate mean, se for dtd_cor and dtd_err
dtd_perf <- llply(names(mod_perf)[1:8],
  .fun = function(x) {
    ddply(
      mod_perf,
      .variables = x,
      .fun = function(y) {
        c(
          min(y$cor),
          quantile(y$cor, 0.25),
          mean(y$cor),
          quantile(y$cor, 0.75),
          max(y$cor),
          min(y$err),
          quantile(y$err, 0.25),
          mean(y$err),
          quantile(y$err, 0.75),
          max(y$err)
        )
    })}
  )

# rename first column for combining, create column for parameter,  then combine
dtd_perf <- lapply(dtd_perf, 
  function(x) { 
    Parameter <- names(x)[1]
    names(x)[1] <- 'Level'
    x[,1] <- factor(x[,1])
    Parameter <- rep(Parameter, nrow(x))
    x <- data.frame(Parameter, x)
    x
    }
  )
dtd_perf <- do.call('rbind', dtd_perf)
names(dtd_perf) <- c('Parameter', 'Level', 'Min cor', 'Low cor', 'Mean cor', 'High cor', 'Max cor', 'Min err', 'Low err', 'Mean err', 'High err', 'Max err')

# subset by DO time series conditions
to_tab <-dtd_perf[!dtd_perf$Parameter %in% c('dec_time', 'hour', 'Tide'), ]

# names for row categories in table
Parms <- c('Tidal category', '$\\boldsymbol{DO_{die}}$', 
  '$\\boldsymbol{DO_{adv}}$',  
  '$\\boldsymbol{\\epsilon_{pro}}$', 
  '$\\boldsymbol{\\epsilon_{obs}}$'
  )
tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Summary (range, mean, percentiles) of correlations and error estimates comparing detided and biological \\ac{DO} time series for different simulation parameters (tidal category, $DO_{die}$, $DO_{adv}$, $\\epsilon_{pro}$, $\\epsilon_{obs}$).  Values represent a combination of results from multiple simulations with the parameter value held constant for each row (e.g., row one is a summary of all simulations for which the tidal category was diurnal).'

@@

latex( 
  tab,
  file = '',
  where = 'h',
  rowlabel = 'Parameter',
#   insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = Parms,
  n.rgroup = rep(3, 5),
  cgroup = c('Correlation', 'RMSE'),
  n.cgroup = c(5, 5),
  rowname = rows,
  colheads=rep(c('Min', '25\\textsuperscript{th}', 'Mean', '75\\textsuperscript{th}', 'Max'),2),
  label = 'tab:dtd_perf1'
  )
@

% summary of simulation performance for detided and biological, window widths
<<dtd_perf2, cache = F, echo = F, eval = T, results = 'asis'>>=

# calculate mean, se for dtd_cor and dtd_err
dtd_perf <- llply(names(mod_perf)[1:8],
  .fun = function(x) {
    ddply(
      mod_perf,
      .variables = x,
      .fun = function(y) {
        c(
          min(y$cor),
          quantile(y$cor, 0.25),
          mean(y$cor),
          quantile(y$cor, 0.75),
          max(y$cor),
          min(y$err),
          quantile(y$err, 0.25),
          mean(y$err),
          quantile(y$err, 0.75),
          max(y$err)
        )
    })}
  )

# rename first column for combining, create column for parameter,  then combine
dtd_perf <- lapply(dtd_perf, 
  function(x) { 
    Parameter <- names(x)[1]
    names(x)[1] <- 'Level'
    x[,1] <- factor(x[,1])
    Parameter <- rep(Parameter, nrow(x))
    x <- data.frame(Parameter, x)
    x
    }
  )
dtd_perf <- do.call('rbind', dtd_perf)
names(dtd_perf) <- c('Parameter', 'Level', 'Min cor', 'Low cor', 'Mean cor', 'High cor', 'Max cor', 'Min err', 'Low err', 'Mean err', 'High err', 'Max err')

# subset by windows
to_tab <-dtd_perf[dtd_perf$Parameter %in% c('dec_time', 'hour', 'Tide'), ]

# names for row categories in table
Parms <- c('Days', 'Hours', 'Tide')

tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Summary (range, mean, percentiles) of correlations and error estimates comparing detided and biological \\ac{DO} time series for simulations using different half window widths in the weighted regressions (days, hours, and proportion of tidal range).  Values represent a combination of results from multiple simulations with the window value held constant for each row (e.g., row one is a summary of all simulations for which the half window width was one day).'

latex( 
  tab,
  file = '',
  rowlabel = 'Window',
#   insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = Parms,
  n.rgroup = rep(3, 3),
  cgroup = c('Correlation', 'RMSE'),
  n.cgroup = c(5, 5),
  rowname = rows,
  colheads=rep(c('Min', '25\\textsuperscript{th}',  'Mean', '75\\textsuperscript{th}', 'Max'),2),
  label = 'tab:dtd_perf2'
  )
@

@@

% correlations with tide before/after wtreg
<<cor_res, cache = F, echo = F, eval = T, results = 'asis'>>=
######
# table of DO/metab correlations with tide before after, detiding
# note that tide in met_ls is daily average (day or night) of hourly tidal change

# # metab and inst flux data
# load('met_ls.RData')
# # load('met_ls_inst.RData')
# load('case_grds.RData')
# 
# # go through each site for DO cors, use metab list for metab cors
# case_regs <- list.files(getwd(), '_wtreg_[0-9]*.RData')
# cor_res <- alply(matrix(case_regs),
#   1, 
#   .fun = function(x){
#   
#     # load wtreg data
#     load(x)
#     nm <- gsub('.RData', '', x)
#     dat_in <- get(nm)
#       
#     # DO obs v tide
#     do_obs <- with(dat_in, 
#       cor.test(DO_obs, Tide)
#       )
#     
#     # DO dtd v tide
#     do_dtd <- with(dat_in, 
#       cor.test(DO_nrm, Tide)
#       )
#     
#     # get tidal range for metabolic day/night periods from flux_in
#     # for correlation with daily integrated metab
#     tide_rngs <- ddply(dat_in, 
#       .variables = c('met.date'),
#       .fun = function(x){
#         
#         # mean tidal derivative for day hours
#         sunrise <- mean(diff(x[x$variable %in% 'sunrise', 'Tide'], 
#           na.rm = T))
#         
#         # mean tidal derivative for night hours
#         sunset <- mean(diff(x[x$variable %in% 'sunset', 'Tide'], 
#           na.rm = T))
#         if(sunrise == 'Inf') sunrise <- NA
#         if(sunset == 'Inf') sunset <- NA
#         
#         # mean tidal derivative for metabolic day
#         daytot <- mean(diff(x$Tide, na.rm = T))
#         
#         c(daytot, sunrise, sunset)
#         
#         }
#       )
#     names(tide_rngs) <- c('Date','daytot', 'sunrise', 'sunset')
#     
#     # get metab data from list
#     dat_in <- met_ls[[x]]
#     dat_in <- merge(dat_in, tide_rngs, by = 'Date', all.x = T)
#     
#     # as list for all metab correlations
#     # Pg values correlated with tidal range during sunlight hours
#     # Rt values correlated with tidal range during night hours
#     # NEM values correlated with metabolic daily tidal range
#     met_cor <- list(
#       
#       Pg_obs = with(dat_in, 
#         cor.test(Pg, sunrise)
#         ),
#     
#       Rt_obs = with(dat_in, 
#         cor.test(Rt, sunset)
#         ),
#     
#       NEM_obs = with(dat_in, 
#         cor.test(NEM, daytot)
#         ),
#     
#       Pg_dtd = with(dat_in, 
#         cor.test(Pg_dtd, sunrise)
#         ),
#     
#       Rt_dtd = with(dat_in, 
#         cor.test(Rt_dtd, sunset)
#         ),
#     
#       NEM_dtd = with(dat_in, 
#         cor.test(NEM_dtd, daytot)
#         )
#       
#       )
#     
#     # DO and metab corrs combined
#     all_ls <- c(do_obs = list(do_obs), do_dtd = list(do_dtd),
#       met_cor)
#     
#     # convert the stats for each wtreg to data frame
#     res_sum <- ldply(all_ls, 
#       function(x) with(x, c(estimate, p.value))
#       )
#     names(res_sum) <- c('var', 'cor', 'pval')
# 
#     res_sum
#     
#   })
# names(cor_res) <- case_regs
# 
# # melt and make separate columns for site and window comb value
# cor_res <- melt(cor_res, id.var = names(cor_res[[1]]))  
# cor_res$site <- gsub('_wtreg_[0-9]*.RData', '', cor_res$L1)
# cor_res$wins <- as.numeric(gsub('^.*_wtreg_|.RData', '', cor_res$L1))
# 
# # merge with case_grds
# case_grds$wins <- as.numeric(row.names(case_grds))
# cor_res <- merge(cor_res, case_grds, by = 'wins', all.x = T)
# 
# # create columns for variable (DO, flux, etc.) and sub variable (obs, dtd)
# cor_res$sub_var <- gsub('^.*_', '', cor_res$var)
# cor_res$var <- gsub('_.*$', '', cor_res$var)
# 
# save(cor_res, file = 'cor_res.RData')
# 
# to_plo <- cor_res
# to_plo$group_var <- paste(to_plo$Tide, to_plo$sub_var)
# to_plo_obs <- to_plo[to_plo$sub_var %in% 'obs', ]
# p1 <- ggplot(to_plo[to_plo$sub_var %in% 'dtd',], 
#     aes(x = dec_time, y = cor, colour = Tide, group = group_var)) +
#   geom_line() + 
#   geom_line(data = to_plo_obs, 
#     aes(x = dec_time, y = cor, group = group_var), 
#     colour = 'black', size = 1) +
#   geom_point(aes(pch = sub_var)) +
#   facet_grid(hour ~ site + var) +
#   ylim(c(-1, 1))

@@

# subset cor_res for window of 30 days, tidal prop 1
cor_res <- cor_res[with(cor_res, dec_time == 4 & hour == 6 & Tide == 1), ]

@@

# reorder rows, columns for plot
to_tab$sub_var <- factor(to_tab$sub_var, levels = c('obs', 'dtd'))
to_tab <- to_tab[with(to_tab, order(site, sub_var)), ]
to_tab <- to_tab[, c('site', 'sub_var', 'do', 'Pg', 'Rt', 'NEM')]

@@

# reorder rows, columns for plot
pvals$sub_var <- factor(pvals$sub_var, levels = c('obs', 'dtd'))
pvals <- pvals[with(pvals, order(site, sub_var)), ]
pvals <- pvals[, c('site', 'sub_var', 'do', 'Pg', 'Rt', 'NEM')]
